---
title: "Question 2 — Temperature data"
author: "Upayan Mazumder"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, message=FALSE, warning=FALSE, fig.width=7, fig.height=4)
library(ggplot2)
library(dplyr)
```

## Question 2 — Temperature data 

Read the provided temperature data and answer the questions.

```{r temperature-data}
temperature <- read.csv("https://mpaldridge.github.io/math1710/data/met-office.csv")
aug_col <- grep("^Aug|August", names(temperature), ignore.case = TRUE, value = TRUE)
aug_col <- aug_col[1]
median_aug <- median(temperature[[aug_col]], na.rm = TRUE)
median_aug
boxplot(temperature[[aug_col]], main = paste("Boxplot of", aug_col), ylab = "Temperature")
```

### (i) What was the median August temperature?

The numeric value is printed above and the boxplot displays the distribution of August temperatures.

```{r april-compare}
apr_col <- grep("^Apr|April", names(temperature), ignore.case = TRUE, value = TRUE)[1]
boxplot(temperature[1:68, apr_col], temperature[69:136, apr_col], names = c("Rows 1-68", "Rows 69-136"),
        main = paste("April temperature: first 68 vs second 68"))
```

### (ii) Boxplot comparison and (iii) comment

Compare the two April boxplots for differences in central tendency and spread; comment in the rendered document about any shift or changes in variability.
