## Question 1 — Student record dataset

Create a synthetic student-record dataset with at least 30 observations and five variables. Summary statistics and graphs follow.

```{r create-student-dataset}
set.seed(123)
n <- 30
student <- data.frame(
  ID = sprintf("S%03d", 1:n),
  Age = sample(18:30, n, replace = TRUE),
  Gender = sample(c("Male","Female","Other"), n, replace = TRUE, prob = c(0.45,0.45,0.10)),
  GPA = round(runif(n, 2.0, 4.0), 2),
  Attendance = round(runif(n, 60, 100), 1),
  Major = sample(c("Math","CS","Physics","Chemistry","Biology"), n, replace = TRUE)
)

head(student)
summary(student)
```

### Graphs

```{r major-bar}
ggplot(student, aes(x=Major)) +
  geom_bar(fill="steelblue") +
  theme_minimal() +
  labs(title="Major distribution", y="Count")
```

Interpretation: the bar chart shows the count of students by major.

```{r gpa-hist}
ggplot(student, aes(x=GPA)) +
  geom_histogram(bins=8, fill="#FB8072", color="black") +
  labs(title="GPA distribution")
```

Interpretation: the histogram shows the GPA spread and central tendency.

```{r age-gender-box}
ggplot(student, aes(x=Gender, y=Age, fill=Gender)) +
  geom_boxplot() +
  labs(title="Age by Gender")
```

```{r gpa-attendance}
ggplot(student, aes(x=Attendance, y=GPA)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) +
  labs(title="GPA vs Attendance")
```

Interpretation: the scatterplot inspects relationship between attendance and GPA.
